## Write a R code to Generate 6X6 matrix (A) using the random numbers between 1 to 100 & generate another 6X6 matrix (B) using random numbers between 500 to 600.
  a. Find the range of matrices A and B.
  b. Find the max value from each row of the matrices A and B
  c. Find the diagonal values of matrices A&B
  d. Multiply matrices A and B
  e. Replace the 4th row of Matrix A with diagonal values of matrix B
  f. Multiply matrices A & B and store the values on X.
  g. Devidethe matrix A with matrix B
```{r}
A <- matrix(sample(1:100,36), nrow = 6)
B <- matrix(sample(500:600,36), nrow = 6)
#a.
range(A)
range(B)
#b
apply(A,1,max)
apply(B,1,max)
#c.
z <- A/B
diag(t(z))
#d.
A%*%B
#e.
A[4, ] <- diag(t(B))
#f.
X <- A%*%B
#g.
A/B
```

## Create a table using dataframe/tibble with the following categories(a to f)
  a. First name,
  b. Second name,
  c. Age,
  d. Occupation,
  e. Place,
  f. Random numbers(between 1 to 10)
And input at least 10 samples(observation) and do the following
  g. Extract the last column (f)
  h. Find the sum, mean and length of the extracted column
```{r}
#a.
fn <- c("Chhuny", "Kimmonyvorn", "Nataly", "Panha", "Dalya", "Menghong", "Bongrong", "Jenny", "Lynan", "Leapheng")
#b.
sn <- c("Am", "Chea", "Chea", "Chean", "Daro", "Chor", "Kit", "Sun", "Thon", "Ty")
#c.
age <- c(20, 19, 20, 21, 22, 19, 20, 20, 20, 19)
#d.
occ <- c("Student", "Student", "Student", "Student", "Student", "Student", "Student", "Student", "Student", "Student")
#e.
pl <- c("PP", "SR", "SR", "PP", "PP", "pp", "KD", "BTB", "BMC", "BTB")
#f.
rn <- sample(1:10,10,replace = TRUE)

tableData <- data.frame(FirstName = fn, LastName = sn, Age = age, Occupation = occ, Place = pl, RandomNumber = rn)
tableData

#g.
lastColumn <- tableData$RandomNumber
lastColumn
#h.
sum(lastColumn)
mean(lastColumn)
length(lastColumn)
```

## Create a .txt file (Minimum: 150 words) with the lastest news (In English) in Cambodia from the official news agency's website (Note: Include the reference link) and do the following
  a. Read the .txt file
  b. Perform the Tokenization & count the words
  c. Identify the most repeated word and replace that word with "TEST"
  d. Perform the Sentiment analysis
```{r}
#a.
readText <- read.delim("text.txt")
#b.
library(tokenizers)
wordsData <- paste0(readText)
tokens <- tokenize_words(wordsData)
count <- count_words(wordsData)
tokens
count
#c.
words <- names(table(tokens))[as.vector(table(tokens))==max(table(tokens))]
wordsCount <- max(table(tokens))
words
wordsCount
subs <- gsub("the", "TEST", tokens)
subs
#d.
library(syuzhet)
sentimentAnalysis <- get_sentiment(tokens, method = "syuzhet")
summary(sentimentAnalysis)
```

## Use dataset(Airline safety https://github.com/fivethirtyeight/data/blob/master/airline-safety/airline-safety.csv) and perform the following
  a. Import and Clean the dataset
  b. Find the x and y variables(axis) from the assigned dataset
  c. Plot the graph using geom_col() and perform the linear model in statistics
  d. Perform the facet with the available columns (Choose the any two variables from the columns)
  e. Use the theme layer to do the following (Note: Based on dataset, name the x and y axis & graph)
    e1. x-axis title = "__", Size = 10, Bold, Text in Green color, Center, space between graph and title = 20
    e2. y-axis title = "__", Size = 10, Bold, Text in Yellow color, Center, space between graph and title = 20
    e3. Graph title = "__", Size = 25, Bold, Text in Blue, Center, space between graph and title = 25
```{r}
#a.
dataset<-read.csv("https://raw.githubusercontent.com/fivethirtyeight/data/master/airline-safety/airline-safety.csv")
dataset
is.na(dataset)
#b.
library(ggplot2)
plot <- ggplot(dataset, aes(x=fatal_accidents_85_99, y=fatalities_85_99)) + 
    xlab("Fatal Accidents") +
    ylab("Fatalities")
plot
#c.
plot <- plot+geom_col()
plot <- plot+geom_smooth(method="lm")
plot
#d.
plot+facet_grid(fatal_accidents_85_99~fatalities_85_99)
plot <- plot+facet_wrap(~fatalities_85_99)
plot
#e.
plot <- plot +
  ggtitle("AirLine") +
  theme(
    axis.title.x=element_text(size=10, color="green", face="bold", margin=margin(t=20,r=20,b=0,l=0)),
    axis.title.y=element_text(size=10, color="yellow", face="bold", margin=margin(t=0,r=20,b=0,l=20)),
    plot.title=element_text(size=25, color="blue", face="bold", hjust = 0.5, margin=margin(t=25,r=0,b=25,l=0))
    )
plot
```

